\documentclass{muratcan_cv}

\setname{Milad}{Molaee}
\setaddress{Tehran/Iran}
\setmobile{+98 912 019 6681}
\setmail{contact@molaee.info}
\setwebsite{molaee.info}
\setposition{Work Student} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/murat-can-karacabey-568a96b1/} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/muratcankaracabey} %you can play with color of the template (red is also nice..)
\setresearchgateaccount{https://github.com/muratcankaracabey}
\setthemecolor{red} %you can play with color of the template (red is also nice..)

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Summary}{%
\vspace{14pt}
\newline\noindent
Milad Molaee is a dedicated PhD student in Chemical Engineering with a robust background in the construction industry. He holds a Bachelor’s degree in Polymer Engineering from Amirkabir University of Technology (Tehran Polytechnic) and a Master’s degree in Chemical Engineering from Iran University of Science and Technology (IUST). Milad has extensive experience working with materials such as concrete, adhesives, grout, and detergents. He previously served as the Manager of the Research and Development Center at Dinokoll, where he led innovative projects and contributed significantly to the company’s advancements. Currently, he focuses on the synthesis and production of various chemical raw materials, with a particular emphasis on hydrogel materials for the oil and gas industry. His PhD project is centered on the usage of hydrogels for corrosion protection, aiming to drive progress and innovation in this critical sector.\ %replace this part with actual text
}
%
%Education
\ \ \newline\section{Education} 
	\vspace{14pt}
    \datedexperience{Tehran Polytechnic}{Sep 2013 - Jul 2018} 
    \explanation{B.Sc. in Polymer Engineering} 
     \explanationdetail{\coloredbullet\ % 
     Modeling of Low-Temperature Water-Gas Shift Reaction in Pd/Ag Membrane Reactor\par %replace this part with actual text
     }\\
    \datedexperience{Iran University of Science and Technology}{Sep 2019 - Jul 2022} 
    \explanation{M.Sc. in Chemical Engineering} 
    \explanationdetail{\coloredbullet\ %
     Molecular Simulation of Gas Adsorption on Single-Wall Carbon Nanotubes\par %replace this part with actual text
     }\\
     \datedexperience{Chemistry and Chemical Research Center of Iran}{Sep 2022 - Present} 
     \explanation{PhD in Chemical Engineering} 
     \explanationdetail{\coloredbullet\ %
     Self-Healing Nanocomposite Hydrogel Loaded with Corrosion Inhibitor for Protection of Q235 Carbon Steel\par %replace this part with actual text
     }
%
% Experience
\ \ \newline\section{Work Experience}
    %
    \vspace{14pt}\datedexperience{Dinokoll Inc.}{Sep 2021 - Jun 2024 / Tehran} 
    \explanation{R\&D Manager}  
    \explanationdetail{\coloredbullet\ %
     At Dinokoll, I was employed for nearly three years, during which time I held the positions of both R\&D unit manager and laboratory manager.\par %replace this part with actual text
     }\\
    %
    \datedexperience{Chemistry \& Chemical Engineering Research Center of Iran (CCERCI)}{Sep 2022 - Present / Tehran} 
    \explanation{Researcher} 
    \explanationdetail{\coloredbullet\ %
     At CCERCI, I have conducted research for nearly two years, with a focus on synthesizing and developing smart hydrogels for various applications. These applications include their use in anti-corrosion methods and materials within the oil and gas industry.\par %replace this part with actual text
     }
%
% Skills
\ \ \newline\section{Skills}

	%
	\vspace{14pt}\newcommand{\skillone}{\createskill{Scientific}{Polymer Chemistry \cpshalf Polymer Characterization \cpshalf Chemical Process Design \cpshalf Reactor Design}}
	%
    \newcommand{\skilltwo}{\createskill{}{Hydrogels \cpshalf Supramolecular Networks \cpshalf Molecular Simulation \cpshalf Molecular Dynamics \cpshalf Monte Carlo}}
    %
    \newcommand{\skillthree}{\createskill{}{Deep Learning \cpshalf Artificial Neural Network \cpshalf Design of experiments}}
    %
    \newcommand{\skillonei}{\createskill{Industrial}{Formulation of Industrial Chemicals \cpshalf Design and Optimization of Chemical Process (Oil, Gas, Petrochamical)}}
    %
    \newcommand{\skilltwoi}{\createskill{}{ Laboratory Data Analysis and Quality Control \cpshalf R\&D Project Managment and Execution}}
    %
    \newcommand{\skillthreei}{\createskill{}{Technical Documentation and Industrial Reporting\cpshalf Scale-up and Troubleshooting of Industrial Processes}}
    %
    \newcommand{\skillfouri}{\createskill{}{Familiarity with Industrial Standards (ISIRI, ISO, ASTM)\cpshalf Cross-functional Collaboration (Production, QC, Sales)}}
    %
    \newcommand{\skillfour}{\createskill{Computer Skills}{Aspen Plus \cpshalf  Hysys \cpshalf COMSOL Multiphysics \cpshalf AutoCAD \cpshalf 3dsMax \cpshalf SolidWorks \cpshalf Matlab \cpshalf OriginPro }}
    %
    \newcommand{\skillfive}{\createskill{}{Design Expert \cpshalf Material Studio \cpshalf Lammps \cpshalf Python \cpshalf C, C++  \cpshalf MS Office \cpshalf \LaTeX}}
    %
    \newcommand{\skillsix}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  Persian \ \ \ \ \textbf{\emph{Fluent:}} \ \ English (B2)\ \ \ \  \textbf{\emph{Beginner:}} \ \  German (A1)}}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \\ \skillonei, \skilltwoi, \skillthreei, \skillfouri, \\ \skillfour, \skillfive, \\ \skillsix}
%
% Experience
\ \ \newline\section{Certificates and Courses}

\ \ \newline\noindent\explanation{\large\textbf{Scientific Courses}}
\newcommand{\extraone}{%
	Introduction to Sustainability. Coursera, Instructor: University of Illinois Urbana-Champaign.
}
%
\newcommand{\extratwo}{%
	Renewable Energy. Coursera, Instructor: University of Colorado Boulder.
}
%
\newcommand{\extrathree}{%
	Sustainable Energy. EdX, Instructor: Massachusetts Institute of Technology.
}
%
\newcommand{\extrafour}{%
	Design of Experiments. Coursera, Instructor: Arizona State University.
}
%
\newcommand{\extrafive}{%
	Python Programming. Pytopia, Instructor: Ali Hejazi.
}
%
\newcommand{\extrasix}{%
	Machine Learning. Pytopia, Instructor: Ali Hejazi.
}
%
\newcommand{\extraseven}{%
	Multi-Objective Optimization with Python. Udemy, Instructor: Navid Shirazi.
}
%
\newcommand{\extraeight}{%
	Protecting the World: Introducing Corrosion Science and Engineering. Instructor: University of Manchester.
}
%
\newcommand{\extranine}{%
	Chemical Hazards and Process Safety. Coursera, Instructor: University of California.
}
%
\newcommand{\listofextras}{\extraone, \extratwo, \extrathree, \extrafour, \extrafive, \extrasix, \extraseven, \extraeight, \extranine}
%
\createbullets{\listofextras}
%
\ \ \newline\noindent\explanation{\large\textbf{Engineering Courses}}
\newcommand{\extraoneo}{%
	AutoCAD Complete Course, Udemy, Instructor: Mike Freeman.
}
%
\newcommand{\extratwoo}{%
	The Complete Course of AutoCAD Plant 3D. Udemy, Instructor: The Tech Courses.
}
%
\newcommand{\extrathreeo}{%
	Comsol Multiphysics: Complete Course 2024. Udemy, Instructor: Digital Courses.
}
%
\newcommand{\extrafouro}{%
	Engineering Project Management. Coursera, Instructor:  Rice University.
}
%
\newcommand{\extrafiveo}{%
	Solar Energy Basics. Coursera, Instructor: The State University of New York.
}
%
\newcommand{\extrasixo}{%
	Solar Energy System Design. Coursera, Instructor: The State University of New York.
}
%
\newcommand{\extraseveno}{%
	Material Processing. Coursera, Instructor: Georgia Institute of Technology.
}
%
\newcommand{\extraeighto}{%
	Physico/Chemical Processes of Environmental Engineering. EdX, Instructor: Purdue University
}
%
\newcommand{\listofextraso}{\extraoneo, \extratwoo, \extrathreeo, \extrafouro, \extrafiveo, \extrasixo, \extraseveno, \extraeighto}
%
\createbullets{\listofextraso}
%
\ \ \newline\noindent\explanation{\large\textbf{Chemical/Petroleum Engineering Courses}}
\newcommand{\extraoneot}{%
	Process/Chemical Engineering. Udemy, Instructors: Velocis Solution, Emil Salimov, and Foad Omar.
}
%
\newcommand{\extratwoot}{%
	Oil \& Gas Industry Operations and Markets. Coursera, Instructor: Duke University.
}
%
\newcommand{\extrathreeot}{%
	Utilities, Safety \& Environmental Care in Oil \& Gas Industry. Coursera, Instructor: L\&T EduTech.
}
%
\newcommand{\extrafourot}{%
	The Complete Course of Aspen HYSYS. Udemy, Instructor: The Tech Courses.
}
%
\newcommand{\extrafiveot}{%
	Aspen Plus V11 MasterClass: from Beginner to Advance User. Udemy, Instructor: WR Training Pro.
}
%
\newcommand{\extrasixot}{%
	Know Read Understand Piping \& Instrumentation Diagrams (P\&IDs). Udemy, Instructor: WR Training.
}
%
\newcommand{\extrasevenot}{%
	Design of Industrial Piping Systems. Coursera, Instructor: L\&T EduTech.
}
%
\newcommand{\extraeightot}{%
	Petroleum Engineering with AI Applications. Coursera, Instructor: L\&T EduTech.
}
%
\newcommand{\listofextrasot}{\extraoneot, \extratwoot, \extrathreeot, \extrafourot, \extrafiveot, \extrasixot, \extrasevenot, \extraeightot}
%
\createbullets{\listofextrasot}

\ \ \newline\section{Projects}

\ \ \newline\noindent\explanation{\large\textbf{Scientific Projects}}
    \newcommand{\aextraone}{%
    Cellulose Derivatives: Synthesis and Characterization. %replace this part with actual text
    }
    %
    \newcommand{\aextratwo}{%
    Synthesis and Characterization of pH-sensitive Hydrogels. %replace this part with actual text
    }
    %
    \newcommand{\aextrathree}{%
    Synthesis and Characterization of Hydrogel-based Anticorrosion Coating. %replace this part with actual text
    }
    %
    \newcommand{\aextrafour}{%
    	Monte Carlo Molecular Simulation of Coordination Polymerization (by C++).\par%replace this part with actual text
    }
    %
    \newcommand{\aextrafive}{%
    	Monte Carlo Molecular Simulation of Gas adsorption on Multi-Wall Carbon Nanotube by Materials Studio.%replace this part with actual text
    }
    %
    \newcommand{\aextrasix}{%
    	Modeling and Optimization of Water-Gas Shift Membrane Reactors by Matlab.%replace this part with actual text
    }
    %
    \newcommand{\aextraseven}{%
    	Mathematical Modeling of Steam Reforming Membrane Reactors (Mathematica).%replace this part with actual text
    }
    %
    \newcommand{\aextraeight}{%
    	NetHub: Deep Learning Package Design and Development (with Python).%replace this part with actual text
    }
    %
    \newcommand{\alistofextras}{\aextraone, \aextratwo, \aextrathree, \aextrafour, \aextrafive, \aextrasix, \aextraseven, \aextraeight}
    %
    \createbullets{\alistofextras}
    
    \ \ \newline\noindent\explanation{\large\textbf{Industrial Projects}}
    \newcommand{\aextraoneo}{%
    	Synthesis and Characterization of Calcium Formate (Industrial-Scale). %replace this part with actual text
    }
    %
    \newcommand{\aextratwoo}{%
    	High-Tech Formulations for Concrete, Grout, and Tile Adhesive (Industrial-Scale). %replace this part with actual text
    }
    %
    \newcommand{\aextrathreeo}{%
    	Detergent Formulation and Development (Industrial-Scale). %replace this part with actual text
    }
    %
    %
    \newcommand{\alistofextraso}{\aextraoneo, \aextratwoo, \aextrathreeo}
    %
    \createbullets{\alistofextraso}
    

\ \ \newline\section{Scientific Articles}
\ \ \newline\noindent\explanation{\large\textbf{Journal Papers}}

\newcommand{\extraoneoo}{%
    	F. Bahmanzadgan, A. Ghaemi, M. Qasemnazhand, and M. Molaee, “Simulation of gas adsorption on single-walled carbon nanotubes”, Sci. Rep., vol. 15, no. 1, p. 15595, May 2025, doi:\href{https://doi.org/10.1038/s41598-025-99988-5}{10.1038/s41598-025-99988-5}. 
    }
    %
    \newcommand{\extraoneooo}{%
    	A. Ghaemi, A. Hemmati, M. Asadollahzadeh, and M. Molaee, “Hydrodynamic behavior of standard liquid-liquid systems in Oldshue–Rushton extraction column; RSM and ANN modeling”, Chem. Eng. Process. - Process Intensif., vol. 168, 2021, doi:\href{https://doi.org/10.1016/j.cep.2021.108559}{10.1016/j.cep.2021.108559}. 
    }
    %
	\newcommand{\listofextrasoo}{\extraoneoo}
	\newcommand{\listofextrasooo}{\extraoneooo}

    %
    \createbullets{\listofextrasoo}
    \createbullets{\listofextrasooo}

\ \ \newline\noindent\explanation{\large\textbf{Conference Proceedings}}

\newcommand{\extracpone}{%
    	M. Molaee, E. Jalali, M. Moshtagh, H. Farahani,“Modeling of Water-Gas shift Membrane Reactor: Investigating the Effect of Design and Operational Parameters on Reactor Performance”, 4th International Conference on Oil, Gas, and Petrochimical, Tehran, Iran, 2017, url:\href{https://civilica.com/doc/640789}{civilica.com/doc/640789}.
    }

\newcommand{\extracptwo}{%
    	M. Molaee, M. Moshtagh, F. Bateni,“Generation and Purification Modeling of Hydrogen by Water-Gas Shift Reaction in Low-Temperature for Fuel Cell Utilization”, 4th National Hydrogen and Fuel Cell Conference, Tehran, Iran, 2017, url:\href{https://civilica.com/doc/641999}{civilica.com/doc/641999}.
    }

\newcommand{\extracpthree}{%
    	M. Moshtagh, M. Molaee, M. Moshtagh, “Modeling of low temperature gas-water shift reaction in packed bed membrane reactor”, 4th National Conference on Chemical, Petrochemical, and Nanotechnology, Tehran, Iran, 2016, url:\href{https://civilica.com/doc/587258}{civilica.com/doc/587258}. 
    }

\newcommand{\extracpfour}{%
    	M. Moshtagh, M. Molaee, M. Moshtagh, “Investigation of Parameters Affecting the Low-Temperature Water-Gas Shift Reaction in a Packed-Bed Membrane Reactor”, 2nd International Conference on Green Engineering and Technologies for a Sustainable Future, Tehtan, Iran, 2016, url:\href{https://civilica.com/doc/596266}{civilica.com/doc/596266}. 
    }

\newcommand{\listofextrasooa}{\extracpone}
\newcommand{\listofextrasoob}{\extracptwo}
\newcommand{\listofextrasooc}{\extracpthree}
\newcommand{\listofextrasood}{\extracpfour}

	\createbullets{\listofextrasooa}
	\createbullets{\listofextrasoob}
	\createbullets{\listofextrasooc}
	\createbullets{\listofextrasood}

\section{}
%
%Footnote
%\createfootnote
\end{document}
